To log or not to log

### 2022-01-30 main.tex

\paragraph{Outline of what we do} 
A natural proposition is therefore to score forecasts on a logarithmic scale, making it easier to model and compare scores across targets by alleviating concerns about skewed forecast scores and also taking into account the multiplicative nature of epidemiological processes. In this paper we will ...

%\begin{enumerate}
%    \item Effects / Interpretation of scoring on a log scale
%    \item Appropriate scales for epidemiological (and possibly other) processes
%    \item Modelling log scores
%\end{enumerate}

@@

The log transformation therefore changes which types of errors (additive or multiplicative) are penalised. The WIS and CRPS computed on the natural scale penalise large absolute errors, regardless of whether the error is large in relative terms. Predicting 101,000 cases instead of the true 100,000 will be treated equally to predicting 2,000 hospitalisations, rather than the 1,000 observed. The WIS and CRPS based on log-transformed values however, penalise relative errors. Forecasting 101,000 rather than 100,000 cases will be treated equally to forecasting 2,020, rather than 2,000 hospitalisations. The score is relative and therefore less dependent on the scale of the forecast quantity, making it easier to compare (relative) performance across different forecast targets, periods and locations.

@@

\section{What happens when you average many scores}

THIS COULD INCLUDE JOHANNES EXAMPLE

COULD ALSO JUST MAKE A SIMULATION. 
YOU TAKE 1000 little counties, combine them to 20 states with different sizes. Then you plot

>>>>

\paragraph{Outline of what we do} 
A natural proposition is therefore to score forecasts on a logarithmic scale, making it easier to model and compare scores across targets by alleviating concerns about skewed forecast scores and also taking into account the multiplicative nature of epidemiological processes. In this paper we will ...
%\begin{enumerate}
%    \item Effects / Interpretation of scoring on a log scale
%    \item Appropriate scales for epidemiological (and possibly other) processes
%    \item Modelling log scores
%\end{enumerate}

@@

The log transformation therefore changes which types of errors (additive or multiplicative) are penalised. The WIS and CRPS computed on the natural scale increase linearly with increasing absolute errors (see Figure \ref{fig:change-in-scores}A, regardless of whether the error is large in relative terms. Predicting 101,000 cases instead of the true 100,000 will be treated equally to predicting 2,000 hospitalisations, rather than the 1,000 observed. The WIS and CRPS based on log-transformed values however, penalise relative errors and increase linearly with an increase in relative errors (see Figure \ref{fig:change-in-scores}D). Forecasting 101,000 rather than 100,000 cases will be treated equally to forecasting 2,020, rather than 2,000 hospitalisations.

@@

\section{Apropriate scales for epidemiological processes}

\paragraph{Modelling on the log scale}

General point: Scores are for a) improving models, b) choosing a model for decision making. 
At least for a): models are multiplicative, so if a model is making error, it's making a multiplicative error. We therefore should score it based on that.

%    - general point about how all processes are modelled %multiplicatively and therefore it might be odd to score them %based on absolute errors
%    - Simulations Sam? 
%    - Adding up several districts - how do scores change? %(Example Johannes) --> relationship between mean and variance %in scores

%THIS COULD INCLUDE JOHANNES EXAMPLE

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\textwidth]{output/figures/SIM-mean-sd-state-size.png}
    \caption{Simulation of the effect of population size with ideal forecasts of a poisson-distributed variable. For each simulated state, we drew 1,000 observations from a poisson distribution with $\lambda = 100 \cdot \text{state size}$ and computed the WIS for an ideal forecast (i.e. the predictive distribution was poisson with $\lambda$ equal to the true $\lambda$ for every state). Left: Mean WIS depending on state size, right: Mean WIS depending on state sizes when scored on a log scale. Plots for the standard deviation, rather than the mean of WIS values look almost identical.}. 
    \label{fig:log-crps-viz}
\end{figure}

The score is relative and therefore less dependent on the scale of the forecast quantity, making it easier to compare (relative) performance across different forecast targets, periods and locations.
